---
title: "Z-Test Report"
output: html_document
params:
  sample_mean: NA
  sample_size: NA
  population_mean: NA
  population_sd: NA
  z_statistic: NA
  significance_level: NA
  conclusion_z_statistic: ""
  z_state: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## STEP 1: CREATING THE HYPOTHESIS


Based on the information provided, the null and alternate hypothesis is given by:
```{r,echo=FALSE}
option <- params$z_state
if(option == "lessthan"){
  h0 = sprintf("$$H_0 : \\mu \\geq %d $$",params$population_mean)
} else if (option == "greaterthan"){
  h0 = sprintf("$$H_0 : \\mu \\leq %d $$",params$population_mean)
} else if (option == "equalto"){
  h0 = sprintf("$$H_0 : \\mu = %d $$",params$population_mean)
}
```

```{r, echo=FALSE, results='asis'}
knitr::asis_output(h0)
```


vs

```{r,echo=FALSE}


if(option == "lessthan"){
  h1 = sprintf("$$H_1 : \\mu < %d $$",params$population_mean)
} else if (option == "greaterthan"){
  h1 = sprintf("$$H_1 : \\mu > %d $$",params$population_mean)
} else if (option == "equalto"){
  h1 = sprintf("$$H_1 : \\mu \\neq %d $$",params$population_mean)
}
```

```{r, echo=FALSE, results='asis'}
knitr::asis_output(h1)
```


```{r}


cat(" T-Test Results\n")
cat("Hypothesized Mean: ", params$population_mean, "\n")
cat("Alpha value:",params$significance_level,"\n")
```

## STEP 2: SELECTION OF THE CRITICAL REGION

Based on the significant level of $\alpha$ = `r params$significant_level`, the rejection region is:
```{r, echo=FALSE}
if (option == "lessthan") {
  CR = "$$R = \\{ z : z < z_{\\alpha} \\} $$"
} else if (option == "greaterthan") {
  CR = "$$R = \\{ z : z > z_{1-\\alpha} \\} $$"
} else if (option == "equalto") {
  CR = "$$R = \\{ z : |z| > z_{1-\\alpha/2} \\} $$"
}
```

```{r, echo=FALSE, results='asis'}
knitr::asis_output(CR)
```


```{r, echo=FALSE}

if (params$z_state == "lessthan") {
  critical_value <- qnorm(as.numeric(params$significant_level), lower.tail = TRUE)
  CR <- paste0("$$R = \\{ z : z < ", round(critical_value, 3), " \\} $$")
} else if (params$z_state == "greaterthan") {
  critical_value <- qnorm(1 - as.numeric(params$significant_level), lower.tail = TRUE)
  CR <- paste0("$$R = \\{ z : z > ", round(critical_value, 3), " \\} $$")
} else if (params$z_state == "equalto") {
  critical_value <- qnorm(1 - as.numeric(params$significant_level) / 2)
  CR <- paste0("$$R = \\{ z : |z| > ", round(critical_value, 3), " \\} $$")
}

```

```{r, echo=FALSE, results='asis'}
knitr::asis_output(CR)
```

## STEP 3: CALCULATION OF THE TEST STATISTICS 

The t-statistics is computed as follows :

$$
Z = \frac{\bar{x} - \mu}{\frac{\sigma}{\sqrt{n}}}
$$
$$
Z = \frac{\bar{x} - `r params$population_mean`}{\frac{`r params$population_sd`}{\sqrt{n}}}
$$




```{r}
cat("Sample Mean: ", params$sample_mean, "\n")
cat("Sample Size: ", params$sample_size, "\n")
cat("Population Mean: ", params$population_mean, "\n")
cat("Population Standard Deviation: ", params$population_sd, "\n")
cat("Z-Statistic: ", params$z_statistic, "\n")
cat("Significant level:" ,params$significance_level,"\n")
```

```{r}
if (params$z_state == "lessthan") {
  critical_value <- qnorm(as.numeric(params$significant_level), lower.tail = TRUE)
  CR <- paste0("$$R = \\{ z : z < ", round(critical_value, 3), " \\} $$")
} else if (params$z_state == "greaterthan") {
  critical_value <- qnorm(1 - as.numeric(params$significant_level), lower.tail = TRUE)
  CR <- paste0("$$R = \\{ z : z > ", round(critical_value, 3), " \\} $$")
} else if (params$z_state == "equalto") {
  critical_value <- qnorm(1 - as.numeric(params$significant_level) / 2)
  CR <- paste0("$$R = \\{ z : |z| > ", round(critical_value, 3), " \\} $$")
}
```
## STEP 5: CONCLUSION BASED ON Z STATISTICS
```{r}
cat("Conclusion based on Z-statistic: ", params$conclusion_z_statistic, "\n")
```
